Maybe Slipstreams

### 2014-03-11 paper.tex
Updated intro a little

\title{Maybe Slipstreams $|$-o-$|$}
\author[*]{Morgan McDermott}
\author[**]{John Carlyle}
\affil[*]{University of flightless dragons}
\affil[**]{University of angry bees}

@@

\section{Introduction}
Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is the programming paradigm based on the key concepts of \textit{behaviors}, \textit{events}, and \textit{reactivity}. Behaviors vary with respect to time and are typically modeled as a stream of values. These values can also be considered events depending on the granularity of the stream. Reactivity is defined as a reaction to an event; when a node recieves a new value it reacts by changing its value. FRP is particularly well suited for transforming data and data structures since it is, by nature, a collection of pure functions.

We solve the problem of interacting with time-varying values can be solved using stream-based FRP, where each computation sends a stream instead of a signal value. A stream is essentially a complete history of the values of a particular computation. Any other computation that needs the current value, or a value from the past, can look at the stream and find the appropriate values. This leads to additional problems like memory usage growing out of control as new values are continually added to the stream and not removed. In some systems garbage collection finds and removes values from streams that are no longer dependencies for other computations. In Elerea \cite{HighOrderStreams}, this is solved by only allowing access to the most recent values in streams.

This paper primarily introduces a way for FRP to interact safely in an environment filled with questionable resources. (What the different sections are for) (Section 1) Section 2 Section 3 Section 4 Section 5 Section 6 Section 7.

@@

Lastly, what happens when two computations wish to change the state of the interface at the same time? How can we allow safe interaction between external state and multiple FRP calculations that wish to modify the state? We solve this using Wormholes as defined by Winograd-Cort \cite{WinogradCort2012HS}

>>>>

\title{Maybe Slipstreams}
\author[*]{Morgan McDermott}
\author[*]{John Carlyle}
\affil[*]{University of flightless dragons}

@@

\section{Introduction}
\subsection{What is FRP}
Functional Reactive Programming, introduced by Fran \cite{ElliottHudak97:Fran}, is a programming paradigm based on the key concepts of time varying values.   These values can also be considered events depending on the granularity of the stream. Reactivity is defined as a reaction to an event; when a node recieves a new value it reacts by changing its value. FRP is particularly well suited for transforming data and data structures since it is, by nature, a collection of pure functions.

\subsection{Why use FRP}
FRP is a useful approach to user interface design because it is declaritive. Most interface design forces you to define exactly how to generate each value. With the time varying values supplied by an FRP network the programmer can choose \textit{what} an interface element is rather than how it is generated. By comosing these values together a higher-level description of what each

\subsection{Problems with FRP}
We solve the problem of interacting with time-varying values can be solved using stream-based FRP, where each computation sends a stream instead of a signal value. A stream is essentially a complete history of the values of a particular computation. Any other computation that needs the current value, or a value from the past, can look at the stream and find the appropriate values. This leads to additional problems like memory usage growing out of control as new values are continually added to the stream and not removed. In some systems garbage collection finds and removes values from streams that are no longer dependencies for other computations. In Elerea \cite{HighOrderStreams}, this is solved by only allowing access to the most recent values in streams.

\subsection{Organization}
This paper primarily introduces a way for FRP to interact safely in an environment filled with hazerdous resources which are difficult to model as a function of time. (What the different sections are for) (Section 1) Section 2 Section 3 Section 4 Section 5 Section 6 Section 7.

@@

Lastly, what happens when two computations wish to change the state of the interface at the same time? How can we allow safe interaction between external state and multiple FRP calculations that wish to modify the state? We solve this using Wormholes as defined by Winograd-Cort \cite{WinogradCort2012HS}.
